Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-06 article.tex
wording + better math

We assess the accuracy of the network inference using the area under
the ROC curve (ROC AUC) obtained by varying the threshold
$\tau$ of the true positive rate $tpr(\tau) = tp(\tau) / (tp(\tau) + fn(\tau))$
as a function of the false positive rate
$fpr(\tau) = tn(\tau) / (tn(\tau) + fp(\tau))$. In section (TODO ref),
we also compare the same methods with the area under the precision-recall
(AUPRC) curve obtained by varying the threshold
$\tau$ of the precision $P(\tau) = tp(\tau) / (tp(\tau) + fp(\tau))$
as a function of the recall $R(\tau) = tp(\tau) / (tp(\tau) + fn(\tau))$,
which is an information retrieval measure.

>>>>

We assess the accuracy of the network inference using the area under
the ROC curve (ROC AUC) obtained by varying the threshold
$\tau$ of the true positive rate $tpr(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$
as a function of the false positive rate
$fpr(\tau) = \frac{tn(\tau)}{tn(\tau) + fp(\tau)}$. In section (TODO ref),
we also compare the same methods with the area under the precision-recall
(AUPRC) curve, an information retrieval metrics, obtained by varying the threshold
$\tau$ of the precision $P(\tau) = \frac{tp(\tau)}{tp(\tau) + fp(\tau)}$
as a function of the recall $R(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$.
